---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Jun Hwang"
date: "July 29. 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Gold Analysis Report

Gold Data Analysis Report enabled developing data products using shiny apps being embeded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.

## Application Overview

- Golds Properties can be analysed using several Parameters.
- Carat,Price,sample size,color Depth are some of the common parameters.
- This Report enables to pick the right parameters for the best gold selection.


## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

 https://junhwang.shinyapps.io/ShinyProject/

Click the link below for compiled project files on gitub repo.

https://github.com/Chopsticks0318/ShinyProject

## Data Used
The data used for this application is gold data set, which contains information about 53940 golds with 10 variables.

```{r, echo=FALSE}
library("ggplot2")
head(diamonds)
```






